Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2015-07-29 sig-alternate.tex
Set-up + Abstract + Structure added

\documentclass{sig-alternate}

@@

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

@@

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

@@

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

\begin{figure}
\centering
\epsfig{file=fly.eps}
\caption{A sample black and white graphic (.eps format).}
\end{figure}

\begin{figure}
\centering
\epsfig{file=fly.eps, height=1in, width=1in}
\caption{A sample black and white graphic (.eps format)
that has been resized with the \texttt{epsfig} command.}
\end{figure}

@@

\begin{figure*}
\centering
\epsfig{file=flies.eps}
\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}

@@

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

>>>>

\documentclass{sig-alternate}
\graphicspath{{figs/}}

@@

\maketitle
\begin{abstract}
In long term interactions between a human and a robot, it is necessary that the agent exhibits some sort of social intelligence to be able to engage the human providing the appropriate response to specific face-to-face situations. In a educational context, this feature becomes a must due to the fact that engagement plays a very important role in the learning process. Therefore, maximizing the interaction time at a high engagement level may provide learning benefits to the children. In this work, a real-time attention tracker based on the head pose estimation using an RGB camera is proposed to be able to identify faults during the interaction and eventually detect low engagement level situations. In this paper we want to show a practical approach to evaluate the engagement that arises from the interaction reporting several experiences in the field, with the robot Nao.
\end{abstract}

@@

\section{Introduction}
The use of robots in the learning activity presents an opportunity for the children
to interact with an embodied, physical agent as part of the learning experience. Furthermore,
the use of robots in handwriting education comes with the potential to engage the child in
meta-cognition through the learning by teaching paradigm, wherein a student takes the role of
a teacher and experiences stronger educational benefits as a result (such as in \cite{Palinscar1984}).

It becomes a useful to capture the significant passive information provided by the
user during the interaction and adapt the situation to it.

\subsection{Approach}
Defining accurately the human field of view in the implementation is a must. Holmqvist in \cite{holmqvist2011eye} specifies that the visual human range is $ \pm  40\degree $ in the horizontal and $ \pm 25\degree $ in the vertical. In \cite{walker1980clinical} Spector provides a more detailed specification for each eye splitting the vertical range into $ 60\degree $ the upper region and $ 75\degree $ the lower one. Moreover, the horizontal range gets separated in $ 60\degree $ inwards (towards the nose) and $ 95\degree $ outwards. In the present implementation, the first approach explained has been chosen representing the field of view using a cone with such dimensions.

We used a commercial RGB camera acquiring images of 640x480 pixels at 25 fps. The camera was located at 5 cm from the center of Nao's feet and its holder was tied to a wood base for stability purposes. Thus, the camera's objective was 9 cm above and $ 40\degree $ inclination with respect to the surface of the table. 
The subjects were typically located 50 cm away from the robot with the first tablet in front and the second one 30 cm to the left of the first one. In the same way, the experimenter was located around 60 cm to the left of the subject. Finally, two observers were located far away from the interaction field to manually assess

in the context of the CoWriter project \footnote{The primary repository is
\url{https://github.com/chili-epfl/cowriter_letter_learning}.}

\subsection{Experimental set-up}
Figure~\ref{drawSetup} illustrates our general experimental setup: a
face-to-face child-robot interaction with an (autonomous) Aldebran's {\sc nao}
robot.

A tactile tablet (with a custom application) is used for both the robot and the
child to write: during a typical round, the child requests the robot to write
something (a single letter, a number or a full word), and push the tablet
towards the robot, the robot writes on the tablet by gesturing the writing (but
without actually physically touching the tablet), the child then pull back the
tablet, corrects the robot's attempt by writing him/herself on top or next to
the robot's writing (see Figure~\ref{fig:diego}), and ``send'' his/her
demonstration to the robot by pressing a small button on the tablet. The robot
``learns'' from this demonstration and tries again.

Since the child is assumed to take on the role of the teacher, we had to ensure
(s)he would be able to manage by him/herself the turn-taking and the overall
progression of the activity (moving to the next letter or word). In our design,
the turn-taking relies on the robot prompting for feedback once it is done with
its writing (simple sentences like ``What do you think?''), and pressing on a
small robot icon on the tablet once the child has finished correcting. In our
experiments, both were easy to grasp for children.

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{drawSetup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
        nao} robot.  The robot writes on the tactile tablet, the child then
        corrects the robot by directly overwriting its letters on the tablet
        with a stylus. An adult (either a therapist or an experimenter,
        depending on the studies), remains next to the child to guide the work
        (prompting, turn taking, etc.). A second tablet allows to choose words
        and the camera captures the subject's head. In red, the focuses of attention
        in the scene.}
    \label{drawSetup}
\end{figure}

Implementing such a system raises several challenges that are discussed in detail in \cite{Hood:2015}.

As we observe the current set-up allow us to intuitively identify several focuses of attention along the interaction such as the two tablets, the robot, the experimenter and the observers located in the diagonal.

\subsection{From face detection to Focus of Attention}

In our approach we use the opensource library dlib\footnote{http://dlib.net} \cite{dlib09}, to detect and extract the skeleton of the subject's face and then, use the obtained landmarkers to calculate the head pose orientation estimation. In this way we can estimate where the subject was looking at. Compared to intrusive hardware like head mounted displays or glasses but also images acquired from an RGB-D cameras for instance, this approach has a clear advantage of simplicity but also becomes accurate enough for general purposes in face-to-face interactions. In addition is able to handle different number and positions of participants in the scenario.

%equations

In this work, head orientation is used to predict a person’s focus of attention in face-to-face interactions. Therefore, we assume that head pose is a reliable marker of the attention focus during a social interaction, in both cases human-human, human-robot. Since we estimate where the subject is looking at based on its head position, several important questions arise:

1. How much the head pose contributes to the real gaze of the subject?
2. Which accuracy can we achieve during a real case scenario in terms of head pose estimation tracking?  
3. How accurate can we predict where the subject is looking at based only on the head pose estimation?
4. How can we evaluate the performance of the children based on the activity?

% Stats from the paper
% Stats from me
% Real vs captured plot
% Real vs expected plot

\begin{figure}
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Typical child-robot interaction scenario during the experiments}

    \label{realSetup}
\end{figure}

\subsection{Head pose contribution to the gaze}

\section{Results}

\section{Discussion}
The results has shown that the percentage of accuracy in the tracking is not only conditioned by the subject's amount of movement, but also by the speed of the same movements: Restless children externalize greater levels of movement decreasing the tracker accuracy. Additionally, several classic computer vision challenges such as the lighting conditions, occlusions and the face angle with respect to the camera are factors that contribute to reduce the accuracy.

@@

\subsection{Figures}

@@

\begin{figure*}
\centering

\caption{A sample black and white graphic (.eps format)
that needs to span two columns of text.}
\end{figure*}

@@

\section{Conclusions}

@@

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!

%\balancecolumns % GM June 2007
\end{document}
